\class : Problem Set \psetnum

### 2022-05-08 531_stars/pset3/solutions.tex
pset3 q3 stars

\question{\textbf{15.4 - Metallicity and Mass Loss Rates}}
\answer{}

\question{\textbf{16.1 - RGB Radii}}
\answer{}

>>>>

\question{\textbf{15.4 - Metallicity and Mass Loss Rates}}
\answer{
    \todo{Need to check code/method with Emily}
}

\question{\textbf{16.1 - RGB Radii}}
\answer{
    From inspection of Figure 16.1 we can find values for $L$ and $T_{\rm eff}$ at the start and end of the RGB phase. This phase starts at C and ends at F. We can then use the fact that
    \begin{equation}
        R = \sqrt{\frac{L}{4 \pi \sigma T_{\rm eff}^4}}
    \end{equation}
    to get the radii. Since I'm in a mood for tables today, let's make another!
    \begin{center}
        \begin{tabular}{c|ccc}
            Stage & $\log (L / \unit{L_\odot})$ & $\log (T_{\rm eff} / \unit{K})$ & $R / \unit{R_{\odot}}$ \\
            \hline
            C (Start of RGB) & 0.4 & 3.7 & 2.1 \\
            F (End of RGB) & 3.4 & 3.48 & 183.1
        \end{tabular}
    \end{center}
}
